GVN-hoist: hoisting expressions from control flow

### 2016-08-04 hoist.tex
rework introduction and add MSSA ref

\maketitle
\begin{abstract}
Code hoisting does not remove redundancies by itself but it enables
removal of redundancies by other passes.  e.g., Enable inlining.
\end{abstract}

@@

graph algorithms \cite{tarjan},
SSA \cite{cytron}
GVN \cite{rosen1988global,click1995global}
CFG, DOM \cite{dragonbook}
SESE, SEME \cite{sese}

>>>>

\maketitle
\begin{abstract}
  Code hoisting identifies identical computations and replaces them with a
  single expression in the common dominator.  Code hoisting is often confused
  with CSE (Common Subexpression Elimination) although is not bound to find
  redundancies within a single basic block.  It could also be confused with PRE,
  although the main goal is not to remove redundancies: it enables removal of
  redundancies by other passes like LICM.  The main goal of code hoisting is to
  reduce code size with added benefit of exposing instruction level parallelism
  and reduced register pressure.
\end{abstract}

@@

graph algorithms \cite{tarjan},
SSA \cite{cytron}
GVN \cite{rosen1988global,click1995global}
CFG, DOM \cite{dragonbook}
SESE, SEME \cite{sese}
MemorySSA \cite{novillo2007memory}
